\cvsection{Contest \& Project Experience}

\begin{cventries}
  \cventry
    {EDA Lab of Prof. Yao-Wen Chang} % Job title
    {Joint Project with Delta} % Organization
    {Taipei, Taiwan} % Location
    {Jul. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The research is about "PCB Layout Design Automation Considering 3D Generalized Design Rules". }
        \item {The project has two parts, placement and trace routing. I am mainly working on the latter part.}
      \end{cvitems}
    }
    
  \cventry
    {Hackthon Combining Software and Hardware, Held by National Taiwan University} % Job title
    {\href{https://github.com/MakeNTU/2021_MakeNTU_Summary}{MakeNTU Cabin Fever}} % Organization
    {Taipei, Taiwan} % Location
    {May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {We design an intelligent and multi-functional alarm, which guarantees people to wake up. We use based boards such as STM32 and Arduino Uno/Nano, modules such as HC-SR04 and L298N, packages like STM32 X-CUBE-AI and Beautiful Soup, to realize the artificial product. }
        \item {Received 1st place in STMicroelectronics Inc. Prize, the Organizer Awards of Best Creativity, and the Most Popular Award.}
        \item {I am also a staff of the contest in 2022, helping organizer to write teaching documents of hardware modules.}
      \end{cvitems}
    }

  \cventry
    {Final Project of Web Programming Class} % Job title
    {\href{https://github.com/Alanhsiu/wp1101_final}{NTU Tutor Web}} % Organization
    {Taipei, Taiwan} % Location
    {Jan. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provide a tutor matching platform for NTU students, with a friendly UI/UX interface and high security for personal information.}
        \item {Use React.js as frontend framework, Restful API and Node.js as backend framework, MongoDB as database, and deploy it on Heroku.}
      \end{cvitems}
    }

  \cventry
    {Final Creative Contests of Cornerstone EECS Design and Implementation} % Job title
    {Smart Trash Bin on Public Transportation} % Organization
    {Taipei, Taiwan} % Location
    {Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {We design a smart trash bin with wheels to replace manpower, which can automatically come at where passengers are and collect trash.}
        \item {The car itself can avoid obstacles and recognize people. We also develop an algorithm to figure out the most efficient path to finish tasks.}
        \item {Received the Best Creativity Award of Robot Car Design Performance.}
      \end{cvitems}
    }

\end{cventries}
